---
title: "HRQoL results"
author: "Eleanor Hayes-Larson"
date: "5/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warnings=FALSE)

if (!require("pacman")) 
  install.packages("pacman", repos='http://cran.us.r-project.org')

p_load("haven", "tidyverse", "magrittr", "foreign", "ggplot2", "gee", "geepack",  
       "survey", "tableone", "openxlsx", "emmeans", "rlang")



```

## Primary analysis: baseline weights and NHATS dementia variable

### Prevalence ratio and difference plots

```{r Main_analysis}
#Load main results
load("C:/Users/ehlarson/Box/NHATS/OUTPUT/HRQOL_pooled.Rdata")
load("C:/Users/ehlarson/Box/NHATS/OUTPUT/predicted_pooled.Rdata")

#Formatting dataset for plotting
#POST CODE REVIEW: removed all "other" references in this code chun (only appeared in lines 32-55)
results_forplot<-pivot_longer(results_all, cols = c("black_est", "hispanic_est"),
                              names_to="race")

results_forplot$LCI<-ifelse(results_forplot$race=="black_est", results_forplot$black_lci, 
                            ifelse(results_forplot$race=="hispanic_est", results_forplot$hispanic_lci,NA))

results_forplot$UCI<-ifelse(results_forplot$race=="black_est", results_forplot$black_uci, 
                            ifelse(results_forplot$race=="hispanic_est", results_forplot$hispanic_uci,NA))

results_forplot<- results_forplot[,c("outcome","race", "dementia", "weight", "measure", "value", "LCI", "UCI")]


results_forplot$outcome2<-NA
results_forplot$outcome2[results_forplot$outcome=="funclimits"]<-"Physical function \nlimitations"
results_forplot$outcome2[results_forplot$outcome=="pain.bother"]<-"Bothered by pain"
results_forplot$outcome2[results_forplot$outcome=="poorhealth.bin"]<-"Fair/poor health"
results_forplot$outcome2[results_forplot$outcome=="prob.dep"]<-"Elevated depressive \nsymptoms"
results_forplot$outcome2[results_forplot$outcome=="prob.anx"]<-"Elevated anxiety \nsymptoms"

results_forplot$race[results_forplot$race=="black_est"] <- "Black vs. white"
results_forplot$race[results_forplot$race=="hispanic_est"] <- "Latino vs. white"




plotresRR<-function(wt){
  ggplot(data=results_forplot[(results_forplot$race=="Black vs. white" | 
                                 results_forplot$race=="Latino vs. white") & 
                                results_forplot$measure=="RR" &
                                results_forplot$weight==wt,])+
    geom_pointrange(aes(x=factor(outcome2, levels = c("Bothered by pain", "Elevated anxiety \nsymptoms",
                                                      "Physical function \nlimitations", "Elevated depressive \nsymptoms",
                                                      "Fair/poor health")), y=value, ymin=LCI, ymax=UCI, group=factor(dementia, levels=c(3,2,1)), 
                        color=factor(dementia, levels=c(1,2,3))), position=position_dodge(width=0.6), size=1, shape=15)+
    xlab("")+ ylab("Prevalence ratio (95% CI)")+ ylim(0.7,2.6)+facet_grid(.~race)+
    scale_color_manual(name="", breaks=c(1,2,3),
                                labels=c("Probable dementia", "Possible dementia","No dementia"), 
                                values=c("navy", "steelblue","lightblue"))+
    theme_bw()+ 
    guides(color = guide_legend(override.aes = list(linetype = 0, size=1)))+
    geom_hline(yintercept=1, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=12), 
          axis.text.y = element_text(size=12), 
          axis.title.x = element_text(size=14), 
          axis.title.y = element_text(size=14), 
          legend.position = "bottom"
    )+ coord_flip()
}

res_un_RR<-plotresRR("unweighted_")
res_bl_RR<-plotresRR("weighted_bl")
res_av_RR<-plotresRR("weighted_av")


plotresRD<-function(wt){
  ggplot(data=results_forplot[(results_forplot$race=="Black vs. white" | 
                                 results_forplot$race=="Latino vs. white") & 
                                results_forplot$measure=="RD" &
                                results_forplot$weight==wt,])+
    geom_pointrange(aes(x=factor(outcome2, levels = c("Bothered by pain", "Elevated anxiety \nsymptoms",
                                                      "Physical function \nlimitations", "Elevated depressive \nsymptoms",
                                                      "Fair/poor health")), y=value, ymin=LCI, ymax=UCI, group=factor(dementia, levels=c(3,2,1)), 
                        color=factor(dementia, levels=c(1,2,3))), position=position_dodge(width=0.6), size=1, shape=15)+
    xlab("")+ ylab("Prevalence difference (95% CI)")+ facet_grid(.~race)+
    scale_color_manual(name="", breaks=c(1,2,3),
                       labels=c("Probable dementia", "Possible dementia","No dementia"), 
                       values=c("navy", "steelblue","lightblue"))+
    theme_bw()+ scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(-0.15,0.3))+
    guides(color = guide_legend(override.aes = list(linetype = 0, size=1)))+
    geom_hline(yintercept=0, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=12), 
          axis.text.y = element_text(size=12), 
          axis.title.x = element_text(size=14), 
          axis.title.y = element_text(size=14), 
          legend.position = "bottom"
    )+ coord_flip()
}

res_un_RD<-plotresRD("unweighted_")
res_bl_RD<-plotresRD("weighted_bl")
res_av_RD<-plotresRD("weighted_av")


figures<-list(res_un_RR=res_un_RR, res_av_RR=res_av_RR, res_bl_RR=res_bl_RR, 
              res_un_RD=res_un_RD, res_av_RD=res_av_RD, res_bl_RD=res_bl_RD)

for (i in 1:length(figures)){
  ggsave(filename=paste0("C:/Users/ehlarson/Box/NHATS/OUTPUT/FIGURES/",names(figures)[i],".jpg"), 
         plot=eval(parse_expr(names(figures[i]))), dpi="retina", width = 6.5)
}

res_bl_RR
res_bl_RD
```


### Predicted prevalence plots


```{r}
#POST CODE REVIEW: removed all "other" references in this code chun (only appeared in lines 133-162)
pred_forplot<-pivot_longer(pred_all, cols = c("white_est", "black_est", "latino_est"),
                           names_to="race")

pred_forplot$LCI<-ifelse(pred_forplot$race=="white_est", pred_forplot$white_LCI,
                         ifelse(pred_forplot$race=="black_est", pred_forplot$black_LCI, 
                                ifelse(pred_forplot$race=="latino_est", pred_forplot$latino_LCI,NA)))

pred_forplot$UCI<-ifelse(pred_forplot$race=="white_est", pred_forplot$white_UCI,
                         ifelse(pred_forplot$race=="black_est", pred_forplot$black_UCI, 
                                ifelse(pred_forplot$race=="latino_est", pred_forplot$latino_UCI,NA)))


pred_forplot<- pred_forplot[,c("outcome","race", "dementia", "value", "LCI", "UCI")]


pred_forplot$outcome2<-NA
pred_forplot$outcome2[pred_forplot$outcome=="funclimits"]<-"Physical function limitations"
pred_forplot$outcome2[pred_forplot$outcome=="pain.bother"]<-"Bothered by pain"
pred_forplot$outcome2[pred_forplot$outcome=="poorhealth.bin"]<-"Fair/poor health"
pred_forplot$outcome2[pred_forplot$outcome=="prob.dep"]<-"Elevated depressive symptoms"
pred_forplot$outcome2[pred_forplot$outcome=="prob.anx"]<-"Elevated anxiety symptoms"

pred_forplot$outcome2<-factor(pred_forplot$outcome2, levels = c("Fair/poor health", "Elevated depressive symptoms",
                                                                "Physical function limitations", 
                                                                "Elevated anxiety symptoms", "Bothered by pain"))

pred_forplot$race[pred_forplot$race=="white_est"] <- "White"
pred_forplot$race[pred_forplot$race=="black_est"] <- "Black"
pred_forplot$race[pred_forplot$race=="latino_est"] <- "Latino"


pred_prev_blwt_dem_byrace<-ggplot(data=pred_forplot[pred_forplot$race %in% c("White", "Black", "Latino"),])+
  geom_col(aes(x=race, y=value, group=factor(dementia), 
               fill=factor(dementia)), width=0.75, position=position_dodge(width=.75))+
  geom_errorbar(aes(x=race, ymin=LCI, ymax=UCI, group=factor(dementia)), width=0.5, position=position_dodge(width=0.75))+
  xlab(NULL)+ ylab("Standardized predicted prevalence (95% CI)")+ 
  facet_wrap( ~ outcome2, ncol=1)+
  scale_fill_manual(name="", labels=c("Probable dementia", "Possible dementia", "No dementia"), values=c("navy", "steelblue", "lightblue"))+
  theme_bw()+ scale_y_continuous(labels = scales::percent_format(accuracy=1), limits=c(0,0.75))+
  geom_hline(yintercept=0, colour="black", lwd=0.5) +
  theme(axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), 
        axis.title.x = element_text(size=16), 
        axis.title.y = element_text(size=16),
        strip.text.x = element_text(size = 12),
        legend.position = "bottom"
  )

pred_prev_blwt_dem_byrace

ggsave(filename=paste0("C:/Users/ehlarson/Box/NHATS/OUTPUT/FIGURES/pred_prev_blwt_dem_byrace.jpg"), 
       plot=pred_prev_blwt_dem_byrace, dpi="retina", width=5, height=9)
```

## Sensitivity analyses

### Unweighted, NHATS dementia variable

```{r sens_un, echo=FALSE}
res_bl_RR
res_bl_RD
```

### Average weights, NHATS dementia variable

```{r sens_av}

res_av_RR
res_av_RD
```

### Baseline weights, race/ethnicity-specific dementia variable

```{r sens_dem}
#Load main results
load("C:/Users/ehlarson/Box/NHATS/OUTPUT/HRQOL_pooled_sens.Rdata")
load("C:/Users/ehlarson/Box/NHATS/OUTPUT/predicted_pooled_sens.Rdata")

#POST CODE REVIEW: removed all "other" references in this code chun (only appeared in lines 212-235)
results_forplot<-pivot_longer(results_all, cols = c("black_est", "hispanic_est"),
                              names_to="race")

results_forplot$LCI<-ifelse(results_forplot$race=="black_est", results_forplot$black_lci, 
                            ifelse(results_forplot$race=="hispanic_est", results_forplot$hispanic_lci,NA))

results_forplot$UCI<-ifelse(results_forplot$race=="black_est", results_forplot$black_uci, 
                            ifelse(results_forplot$race=="hispanic_est", results_forplot$hispanic_uci,NA))

results_forplot<- results_forplot[,c("outcome","race", "dementia", "weight", "measure", "value", "LCI", "UCI")]


results_forplot$outcome2<-NA
results_forplot$outcome2[results_forplot$outcome=="funclimits"]<-"Physical function \nlimitations"
results_forplot$outcome2[results_forplot$outcome=="pain.bother"]<-"Bothered by pain"
results_forplot$outcome2[results_forplot$outcome=="poorhealth.bin"]<-"Fair/poor health"
results_forplot$outcome2[results_forplot$outcome=="prob.dep"]<-"Elevated depressive \nsymptoms"
results_forplot$outcome2[results_forplot$outcome=="prob.anx"]<-"Elevated anxiety \nsymptoms"

results_forplot$race[results_forplot$race=="black_est"] <- "Black vs. white"
results_forplot$race[results_forplot$race=="hispanic_est"] <- "Latino vs. white"





plotresRR<-function(wt){
  ggplot(data=results_forplot[(results_forplot$race=="Black vs. white" | 
                                 results_forplot$race=="Latino vs. white") & 
                                results_forplot$measure=="RR" &
                                results_forplot$weight==wt,])+
    geom_pointrange(aes(x=factor(outcome2, levels = c("Bothered by pain", "Elevated anxiety \nsymptoms",
                                                      "Physical function \nlimitations", "Elevated depressive \nsymptoms",
                                                      "Fair/poor health")), y=value, ymin=LCI, ymax=UCI, group=factor(dementia, levels=c(3,2,1)), 
                        color=factor(dementia, levels=c(1,2,3))), position=position_dodge(width=0.6), size=1, shape=15)+
    xlab("")+ ylab("Prevalence ratio (95% CI)")+ ylim(0.7,2.7)+facet_grid(.~race)+
    scale_color_manual(name="", breaks=c(1,2,3),
                       labels=c("Probable dementia", "Possible dementia","No dementia"), 
                       values=c("tan4", "tan3", "tan1"))+
    theme_bw()+ 
    guides(color = guide_legend(override.aes = list(linetype = 0, size=1)))+
    geom_hline(yintercept=1, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=12), 
          axis.text.y = element_text(size=12), 
          axis.title.x = element_text(size=14), 
          axis.title.y = element_text(size=14), 
          legend.position = "bottom"
    )+ coord_flip()
}


res_un_RR<-plotresRR("unweighted_")
res_bl_RR<-plotresRR("weighted_bl")
res_av_RR<-plotresRR("weighted_av")


plotresRD<-function(wt){
  ggplot(data=results_forplot[(results_forplot$race=="Black vs. white" | 
                                 results_forplot$race=="Latino vs. white") & 
                                results_forplot$measure=="RD" &
                                results_forplot$weight==wt,])+
    geom_pointrange(aes(x=factor(outcome2, levels = c("Bothered by pain", "Elevated anxiety \nsymptoms",
                                                      "Physical function \nlimitations", "Elevated depressive \nsymptoms",
                                                      "Fair/poor health")), y=value, ymin=LCI, ymax=UCI, group=factor(dementia, levels=c(3,2,1)), 
                        color=factor(dementia, levels=c(1,2,3))), position=position_dodge(width=0.6), size=1, shape=15)+
    xlab("")+ ylab("Prevalence difference (95% CI)")+ facet_grid(.~race)+
    scale_color_manual(name="", breaks=c(1,2,3),
                       labels=c("Probable dementia", "Possible dementia","No dementia"), 
                       values=c("tan4", "tan3", "tan1"))+
    theme_bw()+ scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(-0.15,0.4))+
    guides(color = guide_legend(override.aes = list(linetype = 0, size=1)))+
    geom_hline(yintercept=0, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=12), 
          axis.text.y = element_text(size=12), 
          axis.title.x = element_text(size=14), 
          axis.title.y = element_text(size=14), 
          legend.position = "bottom"
    )+ coord_flip()
}


res_un_RD<-plotresRD("unweighted_")
res_bl_RD<-plotresRD("weighted_bl")
res_av_RD<-plotresRD("weighted_av")


figures<-list(res_un_RR=res_un_RR, res_av_RR=res_av_RR, res_bl_RR=res_bl_RR, 
              res_un_RD=res_un_RD, res_av_RD=res_av_RD, res_bl_RD=res_bl_RD)

for (i in 1:length(figures)){
  ggsave(filename=paste0("C:/Users/ehlarson/Box/NHATS/OUTPUT/FIGURES/SENS/",names(figures)[i],"_sens.jpg"), 
         plot=eval(parse_expr(names(figures[i]))), dpi="retina", width=6.5)
}

res_bl_RR
res_bl_RD

```

#### Predicted prevalence, baseline weights, race/ethnicity-specific dementia

```{r}
#POST CODE REVIEW: removed all "other" references in this code chun (only appeared in lines 315-245)
pred_forplot<-pivot_longer(pred_all, cols = c("white_est", "black_est", "latino_est"),
                           names_to="race")

pred_forplot$LCI<-ifelse(pred_forplot$race=="white_est", pred_forplot$white_LCI,
                         ifelse(pred_forplot$race=="black_est", pred_forplot$black_LCI, 
                                ifelse(pred_forplot$race=="latino_est", pred_forplot$latino_LCI,NA)))

pred_forplot$UCI<-ifelse(pred_forplot$race=="white_est", pred_forplot$white_UCI,
                         ifelse(pred_forplot$race=="black_est", pred_forplot$black_UCI, 
                                ifelse(pred_forplot$race=="latino_est", pred_forplot$latino_UCI,NA)))


pred_forplot<- pred_forplot[,c("outcome","race", "dementia", "value", "LCI", "UCI")]


pred_forplot$outcome2<-NA
pred_forplot$outcome2[pred_forplot$outcome=="funclimits"]<-"Physical function limitations"
pred_forplot$outcome2[pred_forplot$outcome=="pain.bother"]<-"Bothered by pain"
pred_forplot$outcome2[pred_forplot$outcome=="poorhealth.bin"]<-"Fair/poor health"
pred_forplot$outcome2[pred_forplot$outcome=="prob.dep"]<-"Elevated depressive symptoms"
pred_forplot$outcome2[pred_forplot$outcome=="prob.anx"]<-"Elevated anxiety symptoms"

pred_forplot$outcome2<-factor(pred_forplot$outcome2, levels = c("Fair/poor health", "Elevated depressive symptoms",
                                                                "Physical function limitations", 
                                                                "Elevated anxiety symptoms", "Bothered by pain"))

pred_forplot$race[pred_forplot$race=="white_est"] <- "White"
pred_forplot$race[pred_forplot$race=="black_est"] <- "Black"
pred_forplot$race[pred_forplot$race=="latino_est"] <- "Latino"


pred_prev_blwt_dem_byrace<-ggplot(data=pred_forplot[pred_forplot$race %in% c("White", "Black", "Latino"),])+
  geom_col(aes(x=race, y=value, group=factor(dementia), 
               fill=factor(dementia)), width=0.75, position=position_dodge(width=.75))+
  geom_errorbar(aes(x=race, ymin=LCI, ymax=UCI, group=factor(dementia)), width=0.5, position=position_dodge(width=0.75))+
  xlab(NULL)+ ylab("Standardized predicted prevalence (95% CI)")+ 
  facet_wrap( ~ outcome2, ncol=1)+
  scale_fill_manual(name="", labels=c("Probable dementia", "Possible dementia", "No dementia"), values=c("tan4", "tan3", "tan1"))+
  theme_bw()+ scale_y_continuous(labels = scales::percent_format(accuracy=1), limits=c(0,0.75))+
  geom_hline(yintercept=0, colour="black", lwd=0.5) +
  theme(axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), 
        axis.title.x = element_text(size=16), 
        axis.title.y = element_text(size=16),
        strip.text.x = element_text(size = 12),
        legend.position = "bottom"
  )



pred_prev_blwt_dem_byrace

ggsave(filename=paste0("C:/Users/ehlarson/Box/NHATS/OUTPUT/FIGURES/SENS/pred_prev_blwt_dem_byrace_sens.jpg"), 
       plot=pred_prev_blwt_dem_byrace, dpi="retina", width=5, height=9)

```


##Sensitivity analysis for observations with no proxy

### Prevalence ratio and difference plots

```{r Noproxy_analysis}
#Load main results
load("C:/Users/ehlarson/Box/NHATS/OUTPUT/HRQOL_pooled_noproxy.Rdata")
load("C:/Users/ehlarson/Box/NHATS/OUTPUT/predicted_pooled_noproxy.Rdata")

#Formatting dataset for plotting
#POST CODE REVIEW: removed all "other" references in this code chun (only appeared in lines 32-55)
results_forplot<-pivot_longer(results_all, cols = c("black_est", "hispanic_est"),
                              names_to="race")

results_forplot$LCI<-ifelse(results_forplot$race=="black_est", results_forplot$black_lci, 
                            ifelse(results_forplot$race=="hispanic_est", results_forplot$hispanic_lci,NA))

results_forplot$UCI<-ifelse(results_forplot$race=="black_est", results_forplot$black_uci, 
                            ifelse(results_forplot$race=="hispanic_est", results_forplot$hispanic_uci,NA))

results_forplot<- results_forplot[,c("outcome","race", "dementia", "weight", "measure", "value", "LCI", "UCI")]


results_forplot$outcome2<-NA
results_forplot$outcome2[results_forplot$outcome=="funclimits"]<-"Physical function \nlimitations"
results_forplot$outcome2[results_forplot$outcome=="pain.bother"]<-"Bothered by pain"
results_forplot$outcome2[results_forplot$outcome=="poorhealth.bin"]<-"Fair/poor health"
results_forplot$outcome2[results_forplot$outcome=="prob.dep"]<-"Elevated depressive \nsymptoms"
results_forplot$outcome2[results_forplot$outcome=="prob.anx"]<-"Elevated anxiety \nsymptoms"

results_forplot$race[results_forplot$race=="black_est"] <- "Black vs. white"
results_forplot$race[results_forplot$race=="hispanic_est"] <- "Latino vs. white"




plotresRR<-function(wt){
  ggplot(data=results_forplot[(results_forplot$race=="Black vs. white" | 
                                 results_forplot$race=="Latino vs. white") & 
                                results_forplot$measure=="RR" &
                                results_forplot$weight==wt,])+
    geom_pointrange(aes(x=factor(outcome2, levels = c("Bothered by pain", "Elevated anxiety \nsymptoms",
                                                      "Physical function \nlimitations", "Elevated depressive \nsymptoms",
                                                      "Fair/poor health")), y=value, ymin=LCI, ymax=UCI, group=factor(dementia, levels=c(3,2,1)), 
                        color=factor(dementia, levels=c(1,2,3))), position=position_dodge(width=0.6), size=1, shape=15)+
    xlab("")+ ylab("Prevalence ratio (95% CI)")+ ylim(0.7,2.7)+facet_grid(.~race)+
    scale_color_manual(name="", breaks=c(1,2,3),
                                labels=c("Probable dementia", "Possible dementia","No dementia"), 
                                values=c("darkorchid4", "darkorchid3","mediumorchid1"))+
    theme_bw()+ 
    guides(color = guide_legend(override.aes = list(linetype = 0, size=1)))+
    geom_hline(yintercept=1, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=12), 
          axis.text.y = element_text(size=12), 
          axis.title.x = element_text(size=14), 
          axis.title.y = element_text(size=14), 
          legend.position = "bottom"
    )+ coord_flip()
}

res_bl_RR<-plotresRR("weighted_bl")


plotresRD<-function(wt){
  ggplot(data=results_forplot[(results_forplot$race=="Black vs. white" | 
                                 results_forplot$race=="Latino vs. white") & 
                                results_forplot$measure=="RD" &
                                results_forplot$weight==wt,])+
    geom_pointrange(aes(x=factor(outcome2, levels = c("Bothered by pain", "Elevated anxiety \nsymptoms",
                                                      "Physical function \nlimitations", "Elevated depressive \nsymptoms",
                                                      "Fair/poor health")), y=value, ymin=LCI, ymax=UCI, group=factor(dementia, levels=c(3,2,1)), 
                        color=factor(dementia, levels=c(1,2,3))), position=position_dodge(width=0.6), size=1, shape=15)+
    xlab("")+ ylab("Prevalence difference (95% CI)")+ facet_grid(.~race)+
    scale_color_manual(name="", breaks=c(1,2,3),
                       labels=c("Probable dementia", "Possible dementia","No dementia"), 
                       values=c("darkorchid4", "darkorchid3","mediumorchid1"))+
    theme_bw()+ scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(-0.15,0.35))+
    guides(color = guide_legend(override.aes = list(linetype = 0, size=1)))+
    geom_hline(yintercept=0, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=12), 
          axis.text.y = element_text(size=12), 
          axis.title.x = element_text(size=14), 
          axis.title.y = element_text(size=14), 
          legend.position = "bottom"
    )+ coord_flip()
}


res_bl_RD<-plotresRD("weighted_bl")

figures<-list(res_bl_RR=res_bl_RR, 
              res_bl_RD=res_bl_RD)

for (i in 1:length(figures)){
  ggsave(filename=paste0("C:/Users/ehlarson/Box/NHATS/OUTPUT/FIGURES/NOPROXY/",names(figures)[i],".jpg"), 
         plot=eval(parse_expr(names(figures[i]))), dpi="retina", width = 6.5)
}

res_bl_RR
res_bl_RD
```


### Predicted prevalence plots


```{r}
#POST CODE REVIEW: removed all "other" references in this code chun (only appeared in lines 133-162)
pred_forplot<-pivot_longer(pred_all, cols = c("white_est", "black_est", "latino_est"),
                           names_to="race")

pred_forplot$LCI<-ifelse(pred_forplot$race=="white_est", pred_forplot$white_LCI,
                         ifelse(pred_forplot$race=="black_est", pred_forplot$black_LCI, 
                                ifelse(pred_forplot$race=="latino_est", pred_forplot$latino_LCI,NA)))

pred_forplot$UCI<-ifelse(pred_forplot$race=="white_est", pred_forplot$white_UCI,
                         ifelse(pred_forplot$race=="black_est", pred_forplot$black_UCI, 
                                ifelse(pred_forplot$race=="latino_est", pred_forplot$latino_UCI,NA)))


pred_forplot<- pred_forplot[,c("outcome","race", "dementia", "value", "LCI", "UCI")]


pred_forplot$outcome2<-NA
pred_forplot$outcome2[pred_forplot$outcome=="funclimits"]<-"Physical function limitations"
pred_forplot$outcome2[pred_forplot$outcome=="pain.bother"]<-"Bothered by pain"
pred_forplot$outcome2[pred_forplot$outcome=="poorhealth.bin"]<-"Fair/poor health"
pred_forplot$outcome2[pred_forplot$outcome=="prob.dep"]<-"Elevated depressive symptoms"
pred_forplot$outcome2[pred_forplot$outcome=="prob.anx"]<-"Elevated anxiety symptoms"

pred_forplot$outcome2<-factor(pred_forplot$outcome2, levels = c("Fair/poor health", "Elevated depressive symptoms",
                                                                "Physical function limitations", 
                                                                "Elevated anxiety symptoms", "Bothered by pain"))

pred_forplot$race[pred_forplot$race=="white_est"] <- "White"
pred_forplot$race[pred_forplot$race=="black_est"] <- "Black"
pred_forplot$race[pred_forplot$race=="latino_est"] <- "Latino"


pred_prev_blwt_dem_byrace<-ggplot(data=pred_forplot[pred_forplot$race %in% c("White", "Black", "Latino"),])+
  geom_col(aes(x=race, y=value, group=factor(dementia), 
               fill=factor(dementia)), width=0.75, position=position_dodge(width=.75))+
  geom_errorbar(aes(x=race, ymin=LCI, ymax=UCI, group=factor(dementia)), width=0.5, position=position_dodge(width=0.75))+
  xlab(NULL)+ ylab("Standardized predicted prevalence (95% CI)")+ 
  facet_wrap( ~ outcome2, ncol=1)+
  scale_fill_manual(name="", labels=c("Probable dementia", "Possible dementia", "No dementia"), values=c("darkorchid4", "darkorchid3", "mediumorchid1"))+
  theme_bw()+ scale_y_continuous(labels = scales::percent_format(accuracy=1), limits=c(0,0.75))+
  geom_hline(yintercept=0, colour="black", lwd=0.5) +
  theme(axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), 
        axis.title.x = element_text(size=16), 
        axis.title.y = element_text(size=16),
        strip.text.x = element_text(size = 12),
        legend.position = "bottom"
  )

pred_prev_blwt_dem_byrace

ggsave(filename=paste0("C:/Users/ehlarson/Box/NHATS/OUTPUT/FIGURES/NOPROXY/pred_prev_blwt_dem_byrace.jpg"), 
       plot=pred_prev_blwt_dem_byrace, dpi="retina", width=5, height=9)
```
